\Large \bf Byteboy : A Byteman Companion application

### 2017-12-07 final-paper/paper.la_.tex
fix(paper): updated results and observations section

This section will focus on the outcomes of running the automatic rule generation and fuzz test generation functionality on the test programs. The following table showcases Byteboy's ability to create valid rules based on the selected action:
\begin{center}
 \begin{tabular}{||c | c | c||} 
 \hline
 Program & Auto. Generator & Fuzz Test Generator\\ [0.5ex] 
 \hline\hline
 A & Yes & Yes\\ 
 \hline
 BinarySearch & Yes & No\\
 \hline
 InfLoop & Yes & Yes\\
 \hline
 Question3 & Yes & Yes\\ [1ex] 
 \hline
\end{tabular}
\end{center}

@@

In all but one case ({\tt BinarySearch.java}), Byteboy was able to produce a set of rules which could be used to potentially alter program behaviour. For the most part, these rules had little affect on the program's execution, which means that the program is robust enough to deal with unexpected input. In the case of {\tt InfLoop.java}, the generated test actually caused the previously infinite loop to exit, ceasing execution of the program. While we are pleased with the initial results of the fuzz test generator functionality, there are many cases that cannot be properly handled, and we will explain these situations in the Limitations part of this paper.

@@

>>>>

This section will focus on the outcomes of running the automatic rule generation and fuzz test generation functionality on the test programs. The following table showcases Byteboy's ability to create valid rules based on the selected action:
\begin{center}
 \begin{tabular}{||c | c | c||} 
 \hline
 Program & Auto. Generator & Fuzz Test Generator\\ [0.5ex] 
 \hline\hline
 A & Yes & Yes\\ 
 \hline
 BinarySearch & Yes & Yes\\
 \hline
 InfLoop & Yes & Yes\\
 \hline
 Question3 & Yes & Yes\\ [1ex] 
 \hline
\end{tabular}
\end{center}

@@

In all cases, Byteboy was able to produce a set of rules which could be used to potentially alter program behaviour. For the most part, these rules had little affect on the program's execution, which means that the program is robust enough to deal with unexpected input. In the case of {\tt InfLoop.java}, the generated test actually caused the previously infinite loop to exit, ceasing execution of the program. While we are pleased with the initial results of the fuzz test generator functionality, there are many cases that cannot be properly handled, and we will explain these situations in the Limitations part of this paper.

@@

{\tt BinarySearch.java}: This program has a bug in the way it outputs it's results, and while the execution is able to sustain the fuzz test randomized values, the effect on program behaviour cannot be observed.
